%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\clearpage
\missiontitle{Common Rules}

The following rules are to be applied to each mission in each round of
the league.

\begin{columns}
  
\missionheading{Startup Sequence}

At the start of each Combat Patrol match:

\begin{enumerate}\shortlist
\item Setup and clarify terrain on a 4'x4' board

\item Both players exchange their army list or lists
  \begin{enumerate}
  \item Players may bring up to~2 lists to a match
  \item Lists may be designed after receiving each round's match
    opponent
  \end{enumerate}

\item Simultaneously choose which list you'll play
\end{enumerate}

\bigskip\noindent Each match consists of two games.  If the mission is
asymmetric, determine which player will take on which role in the
first game, and then switch roles for the second game.  Note that
players use their chosen army list for both games.

\bigskip
The start of each game proceeds as follows unless the mission notes
otherwise:

\begin{enumerate}\shortlist
\item Determine warlord traits, then psychic powers, and then other
  pre-game effects and choices

\item D6 roll off to select deployment zones

\item Place primary objective markers

\item D6 roll off to choose first or second deployment

\item Deploy main armies in that order

\item Deploy any Infiltrators (pg. 167)

\item Secretly choose and record secondary objectives from the options
  listed for the mission

\item Make any Scout redeployments (pg. 171)

\item Reveal secondary objectives and any related selections or marker
  placements as directed

\item First to deploy chooses to play first or second

\item Seize the Initiative roll, if desired and permitted

\item \emph{Battle!}
\end{enumerate}

\bigskip\noindent Standard objective placement constraints apply
unless noted otherwise by a specific mission.

%\vfill\vbox to 0pt{}
\columnbreak
\missionheading{Mission Rules}

The following special rules are applied to each mission unless noted
otherwise.

\missionsubheading{Reserves.} As defined on page~135 of the main
\emph{Warhammer 40,000} rulebook.

\missionsubheading{Seize the Initiative.} As defined on page~132 of
the main \emph{Warhammer 40,000} rulebook.

\missionsubheading{Variable Game Length.} As defined on page~133 of
the main \emph{Warhammer 40,000} rulebook.

\missionsubheading{All In.}  Units/models in reserve at game end count
as completely destroyed/removed as a casualty.

\missionheading{Tertiary Objectives}

The following tertiary objectives apply in each mission.
\underline{At most~5 total victory points may be earned}
\underline{by a player across all of the tertiary objectives.}

\begin{itemize}
\item \textit{Slay the Warlord.}  If your opponent's Warlord or a Lord
  of War character of theirs has been removed as a casualty or is
  falling back at the end of the game, score~2 victory points.

\item \textit{Linebreaker.}  Score~2 victory points if a model from
  any friendly scoring unit is completely within 12'' of your
  opponent's table edge.

\item \textit{First Blood.}  As defined on page~133 of the main
  \emph{Warhammer 40,000} rulebook.

\item \textit{Special Conditions.}  Any unit, faction, formation, or
  other special rules granting victory points to either player are
  considered tertiary objectives and are included within the~5 point
  cap.
\end{itemize}

\end{columns}
