\documentclass{40k}

\usepackage{pdflscape}
\usepackage{enumitem}

\input{mission-list}

%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\begin{document}


%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\input{common-rules}

%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
% \input{table-setup}

%%----------------------------------------------------------------------
%%----------------------------------------------------------------------

%\input{mission1}

\input{mission2}

%\input{mission3}

%\input{tactical-sheets}

\end{document}

%%----------------------------------------------------------------------
%%----------------------------------------------------------------------

\clearpage

\noindent\begin{minipage}[t][\textheight-6pt][t]{1.0\linewidth}
\vfill  
\centerline{\Huge\emph{Missions will be posted shortly.}}
\vfill
\vbox to 0pt{}
\end{minipage}








\pagetitle{Mission Pack}

\begin{columns}

\missionheading{Army Construction}

Armies must be selected to at most~\underline{750 points}.




\missionheading{Restrictions}

Players will use a single army list for all missions.  No requirements
or constraints are placed on detachments or force organizations beyond
those listed above.  All up to date sources\footnote{Partial list
  maintained by Redcap's Corner and PAGE: \url{http://bit.ly/1uWkFHz}}
are permitted.  Forge World units and armies eligible for standard
\emph{Warhammer 40,000} are permitted.

Models need not be painted, but objective painting scores will be
applied to reward finished armies.

Models must be WYSIWYG, but identifiable and thoughtful conversions
and proxies are welcome.  Contact the tournament organizer(s)
beforehand about any uncertain models.  Indistinguishable or confusing
proxies are not permitted.

\missionheading{Supporting Materials}

You must have an official, legal, complete physical or digital copy on
hand for all army, unit, and other sources you are using.  You should
bring printed copies of relevant pages of any electronic sources.
Don't forget errata and FAQs for your sources.\footnote{Available from
  Games Workshop:
  \url{http://www.games-workshop.com/Rules-Errata}}

You must bring any dice, templates, and markers you need to facilitate
playing your army, as well two typed copies of each of your lists,
with points noted.

For any codex or supplement released within two weeks preceding the
event, players may choose whether to use the old or new edition.  They
may not use both editions of a single source within the event, e.g.,
allying old with new.

%\vfill
%\begin{story}{62pt}{The Shift}
%\end{story}
%\columnbreak

\missionheading{Scoring}%

Match results are determined by scoring primary, secondary, and
tertiary objectives as given for each mission.  The winner is the
player with more victory points at game end.  Players draw if they
have earned equal victory points.  No more than~20 victory points may
be earned per mission.

Pure competition standings, i.e., the Best General prize(s) if
awarded, are determined first by win/draw/loss records and then the
sum total victory points earned across all three missions.

Overall tournament rankings and the primary prize(s) are based on
points earned toward a maximum of~100 available for the day:
\begin{itemize}\shortlist
\item 60 points for match results
\item 25 points for painting and craftsmanship
\item 15 points for sportsmanship
\end{itemize}

Match results are a simple sum of the victory points earned in each
mission, up to 20 points each.

Painting and craftsmanship is scored objectively by the judge(s)
applying this rubric to the armies:

\begin{itemize}\shortlist
\item All models assembled and primed: +5 pts
\item All models three-color minimum: +5 pts
\item All models based (paint/flock): +5 pts
\item Advanced painting techniques present (washes, drybrushing, etc): +5 pts
\item Advanced basing techniques present: +5 pts
\end{itemize}

Sportsmanship scores include two components:
\begin{itemize}\shortlist
\item The sum of sportsmanship scores given after each mission (9 pts
  available).

\item Players ranking their opponents by most enjoyable to play (6 pts
  available).
\end{itemize}

Please make sure to submit sportsmanship scores as appropriate,
including the final ranking, as otherwise it impairs your opponents'
overall scores!

\end{columns}
